Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-24 snapshot_system/fast14_evaluation.tex
update
paper revisions

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 25 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
We show three snapshot  availability curves as the number of machines failed increases.
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
Curve ``VC(WC)" represents a worst-case  situation that each PDS file system block is shared by all VMs.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB filesystem
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
To obtain VM sharing of file blocs, we perform perfect deduplication over 105 VMs, 
append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case for VC has a higher availability than VO.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed, VO with 93.256\% availability would lose data in 169 VMs 
while VC with 97.763\% loses data for 56 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB.
% because our VM-centric approach
%localizes deduplication.

@@

\end{figure}
}
\begin{table}
    \footnotesize
    \tabcolsep=0.11cm
    \comments{%table here is obsolete, now uses pgfpltostable to generate latex
        \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        \multirow{3}{*}{Failures}   & \multicolumn{6}{c|}{Snapshot Availability} \\
                                    %\cline{2-7}
                                    & \multicolumn{3}{c|}{$p=100$} & \multicolumn{3}{c|}{$p=1000$} \\
                                    %\cline{2-7}
                                    & VO & VC & VC(Opt) & VO & VC & VC(Opt) \\
        \hline
        3 & 99.3042 & 99.7740 & 99.7740 & 99.9993 & 99.9998 & 99.9998 \\
        5 & 93.2561 & 97.7627  & 97.7627 & 99.9932 & 99.9978 & 99.9978 \\
        10 & 43.2519 & 76.0940 & 76.1541 & 99.9185 & 99.9736 & 99.9736 \\
        20 & 0.0340 & 5.6139 & 6.4942 & 99.2285 & 99.7490 & 99.7491 \\
        \hline
    \end{tabular}
    }
    \pgfplotstabletypeset[
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{$R_C=4$,$R_C=5$,$R_C=6$, $R_C=9$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

@@

Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of VC without local similarity-based search.
Without this, when an entire
segment is moved to another location on disk (e.g. when a file is rewritten
rather than modified in place), searching only the segment in the same location
in the parent will miss the deduplication opportunity. We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
which leads  about 76\% reduction.
Similarity-guided local search can further reduce the data size
to about 12\% of original size, namely it delivers additional 12\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the  size further to 5.6\% of original size, namely it 
delivers additional 6.4\% reduction.

>>>>

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machine nodes failed in a 100-node cluster and  a 1000-node cluster. 
%Two VC curves use $V_c=1250$ and $V_c=2500$ representing the average number of VMs that share a PDS file system block. 
We assume that every VM points to every filesystem block in the PDS ($V_c=p*V$), which is to be expected when PDS
blocks are sorted by hash, as their order is randomized.
%$V_c=2500$ represents  the absolute worst case for 2500 VMs. 
%The VO curve has  $V_o=6.3$ which is the average number of VMs that share a file system block in our smaller dataset.
%To get this number, we perform perfect deduplication over 105 VMs, append unique chunks to a DFS file and
%count the number of dependencies from a file system block to VM.
%In the scenario of having 2500 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
%Our results show that the VC approach even with $V_c=2500$ has a higher availability than VO.
%For example, with 10 machines failed, VO with 98.5\% availability would lose snapshots of 37 VMs 
%while VC with 99.9\% loses snapshots of 2.5 VMs.
%The key reason is that  $N_1 +N_2 < N_o$, caused by the fact that the VM-centric approach localizes deduplication
%and packs  data blocks for one VM as much as possible.  The extra replication
%for PDS blocks also significantly increases the snapshot availability even when
%a PDS file block is shared by every VM.
%=======
%Figure~\ref{tab:vm-availability} shows the availability of VM snapshots
%as storage nodes fail. 
%We assume a random distirbution of 64MB filesystem
%blocks (FSBs). where FSBs are not randomly distributed availability might
%be improved by limiting the number of storage nodes a particualr VM depends
%on but we take the conservative approach. We compare VO, the expected case for
%VC ($V_c=p*V/2$), and the worst case for VC ($V_c=p*V/2$). We set $V_o=6.3$
%based on measured values in our dataset.
To obtain VO sharing of file blocks, we perform perfect deduplication over 105 VMs, 
append unique chunks to a DFS file and
count the number of dependencies from a file system block to VM.
%In the case of having 2500 or even 25000 VMs, this number can only increase, thus this number represents the best
%case for VO approach. 
Our results show that even the worst case for VC (where $v_c=p*V$) has a higher availability than VO.
%Our VM-centric approach shows significant improvements
%in VM availability.
For example, with 5/100 machines failed and 25 VMs per machine, VO with 93.256\% availability would lose data in 169 VMs 
while VC with 97.763\% loses data for 56 VMs.
The key reason is that for most data in VC, only a single
VM can be affected by the loss of a single FSB. Since most FSBs contain blocks for a single VM, VMs can point to a smaller number of FSBs.
% because our VM-centric approach
%localizes deduplication.

@@

\end{figure}
}
\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{$r_c=4$,$r_c=5$,$r_c=6$, $r_c=9$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

@@

Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of the local similarity-based search in VC.
Without this (i.e. when we only check the parent segment at the same offset), when an entire
segment is moved to another location on disk, for example when a file is rewritten
rather than modified in place, the deduplication opportunity is missed. We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
which leads  about 76\% reduction.
Similarity-guided local search can further reduce the data size
to about 12\% of original size, namely it delivers additional 12\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the  size further to 5.6\% of original size, namely it 
delivers additional 6.4\% reduction.
